Target Markdown

### 2022-05-27 _targets.Rmd
filtering out diplicate vedidks of researchers who received 2 grants (keeping only the record of the first one) -> this is in create_ids_complete function
...and duplicate vedidks of supervisors who supervised more than one grant recipients -> this is in make_ids_complete_vector function, which is also used in get_all_pubs function

    tar_target(final_data,
               calc_final_data(eigen_centr, clustering, ind_topics, ind_pubs),
               format = "qs") #,
     # tar_target(testing,
     #           just_test(eigen_centr, clustering, ind_topics = NULL, ind_pubs = NULL),
     #           format = "qs")

>>>>

    tar_target(final_data,
               calc_final_data(eigen_centr, clustering, ind_topics, ind_pubs),
               format = "qs") #,
     # tar_target(testing,
     #           just_test(db_path),
     #           format = "qs")
